Modelling Structured Societies: a Multi-relational Approach to Context Permeability

### 2015-06-15 doc/main.tex
abstract reviewed

		\begin{abstract}
			The structure of social relations is fundamental for the construction of plausible simulation scenarios. It shapes the way actors interact and create their identity within overlapping social contexts. Each actor interacts in multiple contexts, located within relations that constitute their social space. We present a modelling approach to construct structured agent societies with multiple concomitant social networks. We study the notion of context permeability, using a game in which agents try to achieve global consensus. We design and analyse two different models of permeability. In the first model, agents interact concurrently in multiple social networks. The second model uses a context switching mechanism that adds temporal dynamics to agent interaction. They switch between the different networks spending more or less time in each network. We compare each model and analyse the influence of different social networks regarding the speed of convergence to consensus. We conduct a series of experiments that show the impact of coexisting social networks when designing simulation models. This approach unveils both the limitations of the current modelling approaches and possible research directions for complex social space simulations.
		\end{abstract}

>>>>

		\begin{abstract}
                  The structure of social relations is fundamental for the construction of plausible
                  simulation scenarios. It shapes the way actors interact and create their identity
                  within overlapping social contexts. Each actor interacts in multiple contexts
                  within different types of social relations that constitute their social space. In
                  this article, we present an approach to model structured agent societies with
                  multiple coexisting social networks. We study the notion of \textit{context
                    permeability}, using a game in which agents try to achieve global consensus. We
                  design and analyse two different models of permeability. In the first model,
                  agents interact concurrently in multiple social networks. In the second, we
                  introduce a \textit{context switching} mechanism which adds a dynamic temporal
                  component to agent interaction in the model. Agents switch between the different
                  networks spending more or less time in each one. We compare these models and
                  analyse the influence of different social networks regarding the speed of
                  convergence to consensus. We conduct a series of experiments that show the impact
                  of different configurations for coexisting social networks. This approach unveils
                  both the limitations of the current modelling approaches and possible research
                  directions for complex social space simulations.
		\end{abstract}
